The Uppsala University has a Conflict Data Program (UCDP) which is the oldest and biggest provider of war related data. It is considered as the global reference in terms for armed conflicts studies. Even though this ongoing project operates at a much larger scale than ours we can find some correlations. For instance both our plot and their article show that the number of battle related deaths peaked in 1998 to 2001, remained fairly flat until approximately 2012 and increased since then. Our data is more noisy making it harder to see the general trends but peaks are consistent with the UCDP data.
Another interesting similar work is from the article "War and Peace" from the ourworldindata.com website. Just like them, we can notice that the past was not more peaceful, figure(barchart from 1500 to 2000) shows that a lot of battles took place between 1500 and 2000. We often think that the world has more conflicts now than in the past but data shows that this is not true, this thought is the mere consequence of our human memory that is less reminded of past conflicts than present times ones. Like them, we notice that the number of battles was very high in the 1900-1950 time period, which is consistent with WW2 and that the world has been very peaceful in the second half of the 20th century. Their results for the number of international battle deaths in the 20th century is also consistent with our findings. Namely we observe that the major peaks of casualties are in 1910-1920 and 1935-1950 time ranges, these values are easily explained by the first and second world wars.
However we also have inconsistent values and trends. For instance we observe that the number of war related casualties over time has a tendancy to go down, while it is not the case from the UCDP database. We explain this by the fact that we consider battle related deaths only while they also consider extra battle but within war deaths such as collateral civilian bombarding.


%ref1: http://pcr.uu.se/digitalAssets/667/c_667494-l_1-k_battle-related-deaths-by-type-of-conflict--1989-2016.pdf
%ref2: https://ourworldindata.org/war-and-peace/